Multiphyscis modeling for the Fluoride-salt-cooled High-temperature Reactor (FHR)

### 2018-07-22 paper/main.tex
Updates from ShareLaTeX

Unlike the liquid salt coolant, the solid fuel do not change shape or density in the range of the considered temperatures. The fuel temperature reactivity feedback (also called the Doppler feedback) is mainly due to the Doppler broadening of the microscopic cross-sections of the fuel material.
Therefore, the fuel cross-sections are described by a linear-log function of the fuel temperature. During fast transients such as reactivity induced accidents, the heat does not have time to reach the coolant. The core relies on the temperature reactivity feedback from the fuel inside the TRISO particles to stabilize. It is important to compute the temperature distribution inside TRISO particles and fuel pebbles, and use the temperatures at different depth to compute cross-sections. The cross-sections in the fuel region is expressed in the following form:

\begin{align}
  \hat{\Sigma} (T_{fuel}) = c_0 + c_1(log(T_{fuel}) - log(T_0))
  \label{eq:XS_linear_log}
\end{align}

where $\hat{\Sigma}(T_{fuel})$ is the estimation of a fuel macroscopic cross-section, $T_{fuel}$ is the fuel temperature, or temperature vector in case many temperatures affect the homogenized cross-section in a fuel region, and $c_0$, $c_1$ are the coefficients we search for.

>>>>

Unlike the liquid salt coolant, the solid fuel do not change shape or density in the range of the considered temperatures. The fuel temperature reactivity feedback (also called the Doppler feedback) is mainly due to the Doppler broadening of the microscopic cross-sections of the fuel material.
Therefore, the fuel cross-sections are described by a linear-log function of the fuel temperature. During fast transients such as reactivity induced accidents, the heat does not have time to reach the coolant. The core relies on the temperature reactivity feedback from the fuel inside the TRISO particles to stabilize. It is important to compute the temperature distribution inside TRISO particles and fuel pebbles, and use the temperatures at different depth to compute cross-sections.
